%%% Academic Background and Research Experience (Write for your own )


\indent I first became acquainted with Mr. Hasan Ahmed during the sophomore year, when he enrolled in several of my courses, including Electronics, Signal Processing, Digital Signal Processing, and Optoelectronics, along with their corresponding laboratory sessions. Throughout these courses, he consistently demonstrated strong academic performance, intellectual curiosity, and a sincere commitment to mastering complex engineering concepts. Mr. Ahmed graduated in the 2099 cohort with a top-tier class standing, reflecting both dedication and academic capability.\\

\indent What distinguishes Mr. Ahmed is not only academic excellence but also perseverance and a proactive approach to learning. During the Electronics course, he expressed dissatisfaction with an initial term assessment and actively sought feedback for improvement. He carefully reflected on the guidance provided and worked diligently to strengthen conceptual understanding, which ultimately resulted in a strong final course grade. This progression exemplifies determination and self-motivated learning.

\indent Another notable example occurred during an operational amplifier experiment in the Electronics Laboratory. When practical results deviated from theoretical expectations due to hardware limitations, Mr. Ahmed did not merely report the discrepancies. Instead, he invested significant effort in identifying component constraints and analyzing circuit behavior, ultimately presenting a logical explanation that reconciled theoretical predictions with experimental outcomes. This experience highlighted his analytical rigor, hands-on problem-solving ability, and depth of conceptual understanding.

\indent Mr. Ahmed’s interest in embedded systems and signal processing further underscores his research potential. In the Digital Signal Processing course, he independently completed a project, designing the complete pipeline and achieving strong performance. This project demonstrated his ability to translate theoretical knowledge into practical implementations and reflected readiness for research-oriented work. Mr. Ahmed possesses solid programming skills in MATLAB/C/Python, experience with SPICE-based electronic design tools, and effective proficiency in \LaTeX\ for technical documentation.

\vspace{3mm}
